---
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/jjesusfilho/cidades.svg?branch=master)](https://travis-ci.org/jjesusfilho/cidades)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(knitr.table.format = "html") 
```
# cidades

The goal of cidades is to download indicators of Brazilian cities from the
Brazilian National Institute of Geography and Statistics, aka IBGE.

## Installation

You can install cidades from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jjesusfilho/cidades")
```

## Usage

The only function returns a tibble with the indicators from the state cities.

```{r eval=FALSE}
pop_ac<-city_indicators(uf="ac",indicators=25207)

```


There are 28 indicators put available by IBGE. You can load them via:

``` {r eval=FALSE,echo=TRUE}
data(df_indicator)
```

And also check them below:

```{r echo=FALSE, message=FALSE, warning=FALSE }
data("df_indicators")
library(knitr)
library(kableExtra)
kable(df_indicators, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```




