---
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/abjur/brcities.svg?branch=master)](https://travis-ci.org/abjur/brcities)
[![Coverage status](https://codecov.io/gh/abjur/brcities/branch/master/graph/badge.svg)](https://codecov.io/github/abjur/brcities?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jjesusfilho/brcities?branch=master&svg=true)](https://ci.appveyor.com/project/jjesusfilho/brcities)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(knitr.table.format = "html") 
```
# brcities

The goal of brcities is to download indicators of Brazilian cities from the
Brazilian National Institute of Geography and Statistics, aka IBGE. It also downloads city's demographic data from Fundação Seade in São Paulo.

## Installation

You can install brcities from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("abjur/brcities")
```

## Usage

The `city_indicators()` function returns a tibble with the indicators from the state cities. A list of all indicators is found at the end of this readme.

```{r eval=FALSE}
pop_ac<-city_indicators(uf="ac",indicators=25207)

```

If you want data from São Paulo's state, check the documentation for `seade_imp()` function. It provides lots of demographic indicators.

## Datasets

The package provides three datasets: `city_code` containing IBGE code for every Brazilian city,  `state_code` containing IBGE code for every federative unity (states + the federal district), and `df_indicators` with the IBGE indicator's numbers.

## IGBE's indicators

There are 28 indicators put available by IBGE. You can load them via:

``` {r eval=FALSE,echo=TRUE}
data(df_indicator)
```

And also check them below:

```{r echo=FALSE, message=FALSE, warning=FALSE }
data("df_indicators")
library(knitr)
library(kableExtra)
kable(df_indicators, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```




